Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-04-03 main/doc/building_scope.tex

\begin{itemize}
\item
If property \code{chord.reuse.scope} has value \code{true} and the files specified by properties
\code{chord.classes.file} and \code{chord.methods.file} exist,
then Chord regards those files as specifying the classes and methods, respectively,
to be regarded as reachable.  The format
of the classes file is a fully-qualified class name per line (e.g., \code{foo.bar.Main}).  The format
of the methods file is an entry of the form \code{<method name>:<method descriptor>@<class name>} per line,
specifying the method's name, the method's descriptor, and the method's declaring class
(e.g., \code{main:([Ljava/lang/String;)V@foo.bar.Main+}).
Chord throws a runtime exception if the declaring class of a method in the methods file is not
specified in the classes file.

@@

\begin{itemize}
\item
The \code{rta} value instructs Chord to compute the analysis scope statically using Rapid Type Analysis.
\item
The \code{dynamic} value instructs Chord to compute the analysis scope dynamically, by running the program
and observing using JVMTI the classes that are loaded at run-time.
The number of times the program is run and the command-line arguments to be supplied to
the program in each run is specified by properties \code{chord.run.ids} and
\code{chord.args.<id>} for each run ID \code{<id>}.  By default, the program is run only once, using run ID \code{0},
and without any command-line arguments.
Only classes loaded in some run are regarded as reachable but {\it all} methods of each loaded class are regarded
as reachable regardless of whether they were invoked in the run.
The rationale behind this decision is to both reduce run-time overhead of JVMTI and to increase the
predictive power of program analyses performed using the computed analysis scope.
\end{itemize}
\end{itemize}

The default value of property \code{chord.reuse.scope} is \code{false} and that of
property \code{chord.scope.kind} is \code{rta}.
The default values of properties \code{chord.classes.file} and \code{chord.methods.file} are
\code{{chord.out.dir}/classes.txt} and \code{{chord.out.dir}/methods.txt}, respectively,
where property \code{chord.out.dir} defaults to \code{{chord.work.dir}/chord_output/},
and property \code{chord.work.dir} defaults to the current working directory.

>>>>

\begin{itemize}
\item
If property \code{chord.reuse.scope} has value \code{true} and the files specified by properties
\code{chord.classes.file} and \code{chord.methods.file} exist,
then Chord regards those files as specifying the classes and methods, respectively,
to be regarded as reachable.  The format
of the classes file is a fully-qualified class name per line (e.g., \code{foo.bar.Main}).  The format
of the methods file is an entry of the form \code{<method name>:<method descriptor>@<class name>} per line,
specifying the method's name, the method's descriptor, and the method's declaring class
(e.g., \code{main:([Ljava/lang/String;)V@foo.bar.Main}).
Chord throws a runtime exception if the declaring class of a method in the methods file is not
specified in the classes file.

@@

\begin{itemize}
\item
The \code{rta} value instructs Chord to compute the analysis scope statically using Rapid Type Analysis.

\item
The \code{dynamic} value instructs Chord to compute the analysis scope dynamically, by running the program
and observing using JVMTI the classes that are loaded at run-time.
The number of times the program is run and the command-line arguments to be supplied to
the program in each run is specified by properties \code{chord.run.ids} and
\code{chord.args.<id>} for each run ID \code{<id>}.  By default, the program is run only once, using run ID \code{0},
and without any command-line arguments.
Only classes loaded in some run are regarded as reachable but {\it all} methods of each loaded class are regarded
as reachable regardless of whether they were invoked in the run.
The rationale behind this decision is to both reduce run-time overhead of JVMTI and to increase the
predictive power of program analyses performed using the computed analysis scope.
\end{itemize}
\end{itemize}

The default value of property \code{chord.reuse.scope} is \code{false} and that of
property \code{chord.scope.kind} is \code{rta}.
The default values of properties \code{chord.classes.file} and \code{chord.methods.file} are
\code{[chord.out.dir]/classes.txt} and \code{[chord.out.dir]/methods.txt}, respectively,
where property \code{chord.out.dir} defaults to \code{[chord.work.dir]/chord_output/},
and property \code{chord.work.dir} defaults to the current working directory.

### 2010-04-03 main/doc/chord_sysprops.tex

\item
\code{chord.lib.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing libraries needed by Chord. \\
{\bf Default value:} \code{{chord.main.dir}/lib/}

\item
\code{chord.main.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of Chord.  It includes the path specified by property \code{chord.java.analysis.path} to allow running user-defined program analyses. \\
{\bf Default value:} See \code{{chord.main.dir}/build.xml}

\item
\code{chord.bddbddb.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of \code{bddbddb}. \\
{\bf Default value:} See \code{{chord.main.dir}/build.xml}

\item
\code{chord.instr.agent.file} \\
{\bf Type:} location \\
{\bf Description:} Shared library implementing Chord instrumentation agent. \\
{\bf Default value:} \code{{chord.main.dir}/lib/libchord_instr_agent.so}

@@

\item
\code{chord.props.file} \\
{\bf Type:} location \\
{\bf Description:} Properties file loaded by \code{{chord.main.dir}/build.xml}.  Any of the below properties, as well as other user-defined properties to be passed to Chord (e.g., for user-defined analyses), may be set in this file.  Each relative (instead of absolute) path element in the value of any property named \code{chord.<...>.path} set in this file is converted to an absolute path element with respect to the directory containing this file. \\
{\bf Default value:} \code{{chord.work.dir}/chord.properties}

@@

\item
\code{chord.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments passed to JVM running Chord. \\
{\bf Default value:} \code{"-showversion -ea -Xmx{chord.max.heap} -Xss{chord.max.stack}"}

@@

\item
\code{chord.build.scope} \\
 bool \\
 Compute analysis scope (i.e., reachable classes and methods)
using algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}.
Program scope is computed regardless of the value of this property if another task (e.g., a
program analysis to be run) needs it.
{\bf Default value:} \code{false} \\

\item
\code{chord.run.analyses} \\
 string list \\
 List of names of program analyses to be run
in order.
{\bf Default value:} \code{""}

\item
\code{chord.print.rels} \\
{\bf Type:} string list \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{{chord.out.dir}/<...>.txt} where \code{<...>} denotes the relation name.  \\
{\bf Default value:} \code{""}

\item
\code{chord.publish.targets} \\
 bool \\
 Publish all targets defined by program analyses in
paths specified by properties \code{chord.java.analysis.path} and
\code{chord.dlog.analysis.path}.
{\bf Default value:} \code{false} \\

\item
\code{chord.main.class} \\
 class \\
 Fully-qualified name of main class of given program
(e.g., \code{com.example.Main}). \\

\item
\code{chord.class.path} \\
{\bf Type:} path \\
 Classpath of given program. \code{{sun.boot.class.path}}
is implicitly appended to it.
{\bf Default value:} \code{{sun.boot.class.path}}

\item
\code{chord.src.path} \\
{\bf Type:} path \\
 Java source path of given program. \\
{\bf Default value:} \code{""}

\item
\code{chord.run.ids} \\
 string list \\
 List of IDs to identify runs of given program.
{\bf Default value:} \code{0}

\item
\code{chord.args.XXX} \\
 string \\
 Command-line argument string to be used for given
program in run having ID \code{XXX}.
{\bf Default value:} \code{""}

@@

\item
\code{chord.reuse.scope} \\
 bool \\
 Treat analysis scope as the classes and methods listed
in files specified by properties \code{chord.classes.file} and \code{chord.methods.file},
respectively. Property \code{chord.scope.kind} is ignored if this property is set to
\code{true} and the two files exist.
{\bf Default value:} \code{false}

\item
\code{chord.check.exclude} \\
 string list \\
 List of prefixes of names of classes and
packages to be excluded by program analyses.
Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."} \\

@@

\item
\code{chord.java.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath containing program analyses written in Java (i.e., \code{@Chord}-annotated classes). \\
{\bf Default value:} \code{{chord.main.dir}/classes/}

\item
\code{chord.dlog.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., \code{*.datalog} and \code{*.dlog} files). \\
{\bf Default value:} \code{{chord.main.dir}/src/dlog/}

\item
\code{chord.reuse.rels} \\
 bool \\
 Construct program relations from BDDs stored on disk
(from a previous run of Chord) whenever possible instead of re-computing them.
{\bf Default value:} \code{false} \\
\item
\code{chord.publish.results} \\
 bool \\
 Publish the results of program analyses in HTML.
Interpretation of this property is analysis-specific.
{\bf Default value:} \code{true} \\

\item
\code{chord.ssa} \\
 bool \\
 Do SSA transformation for all methods deemed reachable by the
algorithm used to compute analysis scope.
{\bf Default value:} \code{true} \\

\item
\code{chord.bddbddb.noisy} \\
 bool \\
 Make \bddbddb\ output debug info when solving Datalog programs.
{\bf Default value:} \code{false} \\

\item
\code{chord.save.maps} \\
 bool \\
 Write to file \code{{chord.bddbddb.work.dir}/<...>.map}
when saving program domain named \code{<...>} (useful for debugging Datalog programs using
\code{debug} target of \code{{chord.main.dir}/build.xml}).
{\bf Default value:} \code{true} \\

\item
\code{chord.trace.pipe} \\
 bool \\
 Implement the dynamic trace file as a POSIX pipe instead of a regular file.
{\bf Default value:} \code{true} \\

\item
\code{chord.trace.block.size} \\
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the dynamic trace file.
{\bf Default value:} \code{4096} \\

@@

\item
\code{chord.out.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory to which Chord dumps all files. \\
{\bf Default value:} \code{{chord.work.dir}/chord_output/}

\item
\code{chord.out.file} \\
{\bf Type:} location \\
{\bf Description:} File to redirect standard output stream during Chord's execution. \\
{\bf Default value:} \code{{chord.out.dir}/log.txt}

\item
\code{chord.err.file} \\
{\bf Type:} location \\
{\bf Description:} File to redirect standard error stream during Chord's execution. \\
{\bf Default value:} \code{{chord.out.dir}/log.txt}

\item
\code{chord.classes.file} \\
{\bf Type:} location \\
{\bf Description:} File from/to which list of classes deemed reachable is read/written. \\
{\bf Default value:} \code{{chord.out.dir}/classes.txt}

\item
\code{chord.methods.file} \\
{\bf Type:} location \\
{\bf Description:} File from/to which list of methods deemed reachable is read/written. \\
{\bf Default value:} \code{{chord.out.dir}/methods.txt}

\item
\code{chord.bddbddb.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory used by \bddbddb\ as its input/output directory. \\
{\bf Default value:} \code{{chord.out.dir}/bddbddb/}

\item
\code{chord.boot.classes.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing instrumented JDK classes used by given program. \\
{\bf Default value:} \code{{chord.out.dir}/boot_classes/}

\item
\code{chord.user.classes.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing instrumented non-JDK classes of given program. \\
{\bf Default value:} \code{{chord.out.dir}/user_classes/}

\item
\code{chord.instr.scheme.file} \\
{\bf Type:} location \\
{\bf Description:} File specifying kind and format of events in dynamic trace file. \\
{\bf Default value:} \code{{chord.out.dir}/scheme.ser}

\item
\code{chord.crude.trace.file} \\
{\bf Type:} location \\
{\bf Description:} Crude dynamic trace file. \\
{\bf Default value:} \code{{chord.out.dir}/crude_trace.txt}

\item
\code{chord.final.trace.file} \\
{\bf Type:} location \\
{\bf Description:} Final dynamic trace file. \\
{\bf Default value:} \code{{chord.out.dir}/final_trace.txt}
\end{enumerate}

>>>>

\item
\code{chord.lib.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing libraries needed by Chord. \\
{\bf Default value:} \code{[chord.main.dir]/lib/}

\item
\code{chord.main.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of Chord.  It includes the path specified by property \code{chord.java.analysis.path} to allow running user-defined program analyses. \\
{\bf Default value:} See \code{[chord.main.dir]/build.xml}

\item
\code{chord.bddbddb.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of \code{bddbddb}. \\
{\bf Default value:} See \code{[chord.main.dir]/build.xml}

\item
\code{chord.instr.agent.file} \\
{\bf Type:} location \\
{\bf Description:} Shared library implementing Chord instrumentation agent. \\
{\bf Default value:} \code{[chord.main.dir]/lib/libchord_instr_agent.so}

@@

\item
\code{chord.props.file} \\
{\bf Type:} location \\
{\bf Description:} Properties file loaded by \code{[chord.main.dir]/build.xml}.  Any of the below properties, as well as other user-defined properties to be passed to Chord (e.g., for user-defined analyses), may be set in this file.  Each relative (instead of absolute) path element in the value of any property named \code{chord.<...>.path} set in this file is converted to an absolute path element with respect to the directory containing this file. \\
{\bf Default value:} \code{[chord.work.dir]/chord.properties}

@@

\item
\code{chord.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments passed to JVM running Chord. \\
{\bf Default value:} \code{"-showversion} \code{-ea} \code{-Xmx[chord.max.heap]} \code{-Xss[chord.max.stack]"}

@@

\item
\code{chord.build.scope} \\
{\bf Type:} bool \\
{\bf Description:} Compute analysis scope (i.e., reachable classes and methods) using algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}.
Program scope is computed regardless of the value of this property if another task (e.g., a program analysis to be run) needs it. \\
{\bf Default value:} \code{false}

\item
\code{chord.run.analyses} \\
{\bf Type:} string list \\
{\bf Description:} List of names of program analyses to be run in order. \\
{\bf Default value:} \code{""}

\item
\code{chord.print.rels} \\
{\bf Type:} string list \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<...>.txt} where \code{<...>} denotes the relation name.  \\
{\bf Default value:} \code{""}

\item
\code{chord.publish.targets} \\
{\bf Type:} bool \\
{\bf Description:} Publish all targets defined by program analyses in paths specified by properties \code{chord.java.analysis.path} and \code{chord.dlog.analysis.path}. \\
{\bf Default value:} \code{false}

\item
\code{chord.main.class} \\
{\bf Type:} class \\
{\bf Description:} Fully-qualified name of main class of given program (e.g., \code{com.example.Main}).

\item
\code{chord.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of given program. \code{[sun.boot.class.path]} is implicitly appended to it. \\
{\bf Default value:} \code{[sun.boot.class.path]}

\item
\code{chord.src.path} \\
{\bf Type:} path \\
{\bf Description:} Java source path of given program. \\
{\bf Default value:} \code{""}

\item
\code{chord.run.ids} \\
{\bf Type:} string list \\
{\bf Description:} List of IDs to identify runs of given program. \\
{\bf Default value:} \code{0}

\item
\code{chord.args.<id>} \\
{\bf Type:} string \\
{\bf Description:} Command-line argument string to be used for given program in run having ID \code{<id>}. \\
{\bf Default value:} \code{""}

@@

\item
\code{chord.reuse.scope} \\
{\bf Type:} bool \\
{\bf Description:} Treat analysis scope as the classes and methods listed in files specified by properties \code{chord.classes.file} and \code{chord.methods.file}, respectively. Property \code{chord.scope.kind} is ignored if this property is set to \code{true} and the two files exist. \\
{\bf Default value:} \code{false}

\item
\code{chord.check.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."}

@@

\item
\code{chord.java.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath containing program analyses written in Java (i.e., \code{@Chord}-annotated classes). \\
{\bf Default value:} \code{[chord.main.dir]/classes/}

\item
\code{chord.dlog.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., \code{*.datalog} and \code{*.dlog} files). \\
{\bf Default value:} \code{[chord.main.dir]/src/dlog/}

\item
\code{chord.reuse.rels} \\
{\bf Type:} bool \\
{\bf Description:} Construct program relations from BDDs stored on disk (from a previous run of Chord) whenever possible instead of re-computing them. \\
{\bf Default value:} \code{false}

\item
\code{chord.publish.results} \\
{\bf Type:} bool \\
{\bf Description:} Publish the results of program analyses in HTML.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{true}

\item
\code{chord.ssa} \\
{\bf Type:} bool \\
{\bf Description:} Do SSA transformation for all methods deemed reachable by the algorithm used to compute analysis scope. \\
{\bf Default value:} \code{true}

\item
\code{chord.bddbddb.noisy} \\
{\bf Type:} bool \\
{\bf Description:} Make \bddbddb\ output debug info when solving Datalog programs. \\
{\bf Default value:} \code{false}

\item
\code{chord.save.maps} \\
{\bf Type:} bool \\
{\bf Description:} Write to file \code{[chord.bddbddb.work.dir]/<...>.map} when saving program domain named \code{<...>} (useful for debugging Datalog programs using \code{debug} target of \code{[chord.main.dir]/build.xml}). \\
{\bf Default value:} \code{true}

\item
\code{chord.trace.pipe} \\
{\bf Type:} bool \\
{\bf Description:} Implement the dynamic trace file as a POSIX pipe instead of a regular file. \\
{\bf Default value:} \code{true}

\item
\code{chord.trace.block.size} \\
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the dynamic trace file. \\
{\bf Default value:} \code{4096}

@@

\item
\code[chord.out.dir] \\
{\bf Type:} location \\
{\bf Description:} Directory to which Chord dumps all files. \\
{\bf Default value:} \code{[chord.work.dir]/chord_output/}

\item
\code{chord.out.file} \\
{\bf Type:} location \\
{\bf Description:} File to redirect standard output stream during Chord's execution. \\
{\bf Default value:} \code{[chord.out.dir]/log.txt}

\item
\code{chord.err.file} \\
{\bf Type:} location \\
{\bf Description:} File to redirect standard error stream during Chord's execution. \\
{\bf Default value:} \code{[chord.out.dir]/log.txt}

\item
\code{chord.classes.file} \\
{\bf Type:} location \\
{\bf Description:} File from/to which list of classes deemed reachable is read/written. \\
{\bf Default value:} \code{[chord.out.dir]/classes.txt}

\item
\code{chord.methods.file} \\
{\bf Type:} location \\
{\bf Description:} File from/to which list of methods deemed reachable is read/written. \\
{\bf Default value:} \code{[chord.out.dir]/methods.txt}

\item
\code{chord.bddbddb.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory used by \bddbddb\ as its input/output directory. \\
{\bf Default value:} \code{[chord.out.dir]/bddbddb/}

\item
\code{chord.boot.classes.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing instrumented JDK classes used by given program. \\
{\bf Default value:} \code{[chord.out.dir]/boot_classes/}

\item
\code{chord.user.classes.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing instrumented non-JDK classes of given program. \\
{\bf Default value:} \code{[chord.out.dir]/user_classes/}

\item
\code{chord.instr.scheme.file} \\
{\bf Type:} location \\
{\bf Description:} File specifying kind and format of events in dynamic trace file. \\
{\bf Default value:} \code{[chord.out.dir]/scheme.ser}

\item
\code{chord.crude.trace.file} \\
{\bf Type:} location \\
{\bf Description:} Crude dynamic trace file. \\
{\bf Default value:} \code{[chord.out.dir]/crude_trace.txt}

\item
\code{chord.final.trace.file} \\
{\bf Type:} location \\
{\bf Description:} Final dynamic trace file. \\
{\bf Default value:} \code{[chord.out.dir]/final_trace.txt}
\end{enumerate}
